\documentclass[addpoints]{exam}

\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{tikz}

% Header and footer.
\pagestyle{headandfoot}
\runningheadrule
\runningfootrule
\runningheader{CS 201 DS II}{Homework 6}{Spring 2018}
\runningfooter{}{Page \thepage\ of \numpages}{}
\firstpageheader{}{}{}

\qformat{{\large\bf Exercise \thequestiontitle}\hfill[\totalpoints\ points]}
\boxedpoints
\printanswers

\title{Habib University\\CS 201 Data Structures II\\Spring 2018}
\author{Don't Grade Me}  % replace with your ID, e.g. sh01703
\date{Homework 6\\\numpoints\ points. Due: --}

\begin{document}
\maketitle

\begin{questions}

  \titledquestion{9.8*}
  Suppose a 2-4 tree, $T$, has $n_e$ external nodes and $n_i$ internal nodes.
  \begin{parts}
    \part[3] What is the minimum value of $n_i$, as a function of $n_e$?
    \part[2] What is the maximum value of $n_i$, as a function of $n_e$?
    \part[5] If $T'$ is a red-black tree that represents $T$, then how many red nodes does $T'$ have?
  \end{parts}

  \titledquestion{9.10}[10]
  Suppose you have two red-black trees $T_1$ and $T_2$ that have the same black height, $h$, and such that the largest key in $T_1$ is smaller than the smallest key in $T_2$. Show how to merge $T_1$ and $T_2$ into a single red-black tree in $O(h)$ time.
  
  \question
  Consider the set of keys $K = \{1,2,3,4,5,6,7,8,9,10,11,12,13,14,15\}$.
  \begin{parts}
    \part[5] Draw a (2,4) tree storing $K$ as its keys using the fewest number of nodes.
    \part[5] Draw a (2,4) tree storing $K$ as its keys using the maximum number of nodes.
  \end{parts}
  \begin{solution}
    % Write your solution here
  \end{solution}

  \question[10]
  For the following statements about red-black trees, provide a justification for each true statement and a counterexample for each false one.
  \begin{parts}
    \part A subtree of a red-black tree is itself a red-black tree.
    \part A node that does not have a sibling is red.
    \part There is a unique (2,4) tree associated with a given red-black tree.
    \part There is a unique red-black tree associated with a given (2, 4) tree.
  \end{parts}

  \question[10]
  Consider a tree $T$ storing 100,000 entries. What is the worst-case height of T in the following cases?
  \begin{parts}
    \part $T$ is a BST.
    \part $T$ is an AVL tree.
    \part $T$ is a (2,4) tree.
    \part $T$ is a red-black tree.
  \end{parts}
\end{questions}

* - The question has been modified from the one in the book.

\end{document}